Exploratory data analysis

### 2021-08-16 slides/data_checking.Rmd
just a couple more shits

```{r}
j_recall %>% 
  mutate(acc_recall = as.integer(acc_recall),
         j_score = j_score - 0.5) %>% 
  lme4::lmer(resp_conf ~ acc_recall * j_score + (1 + acc_recall | subj_num), data = .) %>% 
  summary()
```

@@

```{r}
encoding %>% 
  ggplot(aes(x = resp, fill = category)) +
  geom_histogram(position = "identity", alpha = 0.5) +
  facet_wrap(~subj_num)
```

@@

```{r}
encoding %>% 
  mutate(already_knew = fct_relevel(already_knew, "Did not know this before", "Knew some of this before")) %>% 
  ggplot(aes(x = subj_num, fill = already_knew)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(x = "Participant", y = "# facts already knew", fill = "Prior knowledge") +
  theme_bw()
```

@@

>>>>

```{r}
j_recall %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  mutate(acc_recall = as.integer(acc_recall),
         # so 0.5 is centered
         j_score = j_score - 0.5,
         is_male = gender == "male") %>% 
  lme4::lmer(resp_conf ~ acc_recall * j_score + is_male + (1 + acc_recall | subj_num), data = .) %>% 
  summary()
```

@@

```{r}
encoding %>% 
  ggplot(aes(x = resp, fill = category)) +
  geom_histogram(position = "identity", binwidth = 5, alpha = 0.5)
```

```{r}
encoding %>% 
  ggplot(aes(x = j_score, y = resp, color = category, fill = category)) +
  geom_jitter(alpha = 0.5) +
  geom_smooth(formula = y ~ x, method = "lm")
```

@@

```{r}
encoding %>% 
  mutate(already_knew = fct_relevel(already_knew, "none", "some")) %>% 
  ggplot(aes(x = subj_num, fill = already_knew)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(x = "Participant", y = "# facts already knew", fill = "Prior knowledge") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         interest = (interest / 100) - 0.5,
         j_score = j_score - 0.5) %>% 
  lme4::glmer(acc_recall ~ interest * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
  summary()
```
